---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo = FALSE, eval = TRUE}
library(Group03lab06)
```
This package contains three different approaches to solve the knapsack problem. 

## Inputs for the functions
The input Knapsack objects is generated by the following commands.
```{r, echo = TRUE}
suppressWarnings(RNGversion(min(as.character(getRversion()),"3.5.3")))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
)
```
A small portion of the input generated is
```{r, echo = FALSE}
knapsack_objects[1:8,]
```

The next input is the knapsack size, W
```{r, echo = TRUE}
W = 3500
```
Note that both the inputs should be positive.

## Brute force approach to solve knapsack problem
This method solves the problem by calculating all possible combinations of the items and then selecting the one with maximum value that is less than the given knapsack size W. This function returns the maximum value and the elements. 
An example function call to this function is 
```{r, echo = TRUE, eval = FALSE}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
```{r, echo = FALSE}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```

### Question: How much time does it takes to run the algorithm for n = 16 objects?
Answer: Using system.time(), it can be seen that the time to execute the algorithm for 16 objects is  69.53 ms.

## Dynamic approach to solve knapsack problem
This function also returns the maximum value and the elements. 
An example function call to this function is 
```{r, echo = TRUE, eval = FALSE}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
```
```{r, echo = FALSE}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
```

## Greedy approach to solve knapsack problem
This function also returns the maximum value and the elements. 
An example function call to this function is 
```{r, echo = TRUE, eval = FALSE}
greedy_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
```{r, echo = FALSE}
greedy_knapsack(x = knapsack_objects[1:8,], W = 3500)
```
